Agents and you, a brief summary

### 2015-11-01 agents/summery.tex
added some stuffs about belman the operator.

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{tikz}
\usetikzlibrary{automata,arrows,positioning,calc}
\usepackage{listings}
\usepackage{hyperref}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

@@

\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{tikz}
\usepackage{amssymb}
\usetikzlibrary{automata,arrows,positioning,calc}
\usepackage{listings}
\usepackage{hyperref}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

@@

\subsection{Markov reward}
A \emph{Markov reward process} is a markov process with rewards on
transitions. these rewards are real valued.

Markov rewards processes are also known as \emph{markov reward chain} or
\emph{valued Markov chains}.

example

\[
	P =
\begin{pmatrix}
	0.2	& 0.8 & 0 	& \\
	0.3	& 0	& 0.7	& \\
	0	& 0 & 1	& \\
\end{pmatrix}
\]
With reward matrix:
\[
	R =
\begin{pmatrix}
	1	& 2 & 0 	& \\
	0	& 0	& 3	& \\
	0	& 0 & 0	& \\
\end{pmatrix}
\]

\subsubsection{Total reward}

Let $\omega$ be a realisation of a Markov process:

\[\omega = s_0, s_1, \dots\]

where $s_0$ is a start state.
The rewards that accumulate are $r_1, r_2, \dots$:

\[ s_0 \xrightarrow[\mbox{reward } r_1]{} s_1 \xrightarrow[\mbox{reward } r_2]{} s_2\]

\paragraph{Definition}

$r_k | (s_0=1) : $ reward at kth step, given $s_0 = i$.
$R|(s_0=i),$ the \emph{total reward} : $(r_1 + r_2 \dots)|s_0=i,$
$V(i),$ the \emph{value} of state i : $E[R|s_0=i]$.

\subsection{The bellman equation}

\[V(i)=\sum_{all\mbox{\ }j} p_{ij}[r_{ij} + V(j)]\]

This system of linear equations enables us to compute state values in two
ways, by using algebra or by using iteration. Iteration you just wait until
convergence within a specified range. For this course iteration is enough.

\subsection{Utility pump}
A utility pump is a MRP in which at least one recurrent state possesses a
non-zero reward.
\subsubsection{Discount factor}
A \emph{dicsount factor} is a real number $0 \le \gamma < 1$. it represents
the probability to survive from one state to the next.

\paragraph{remarks} The discount factor is constant. The discount factor
does not impose a fixed cuttoff bound. It is a probablistic concept.

\subsubsection{Discounted reward}
Suppose a discount factor $0 \le \gamma < 1$. Then

\[V(i)=\sum_{all\mbox{\ }j} p_{ij}[r_{ij} + \gamma V(j)]\]

for every state $i$.

\paragraph{definition} A \emph{valuation} is a vector

\[v=Def
\begin{pmatrix}
	v(1) \\
	\vdots \\
	v(n)
\end{pmatrix}
\in \mathbb{R}^n
\]

\paragraph{definition} The \emph{expected immediate reward} at state $i$ is
the by $P_{ij}$ - probabilities weighted averaga of the $r_{ij}$ rewards:

\[C(i)=Def\sum_{all \mbox{\ }j} p_{ij} r_{ij} \]

The (vertical) vector of expected immediate rewards is denoted by $C$.

\paragraph{definition} The \emph{Bellman operator}:

\[B_p : \mathbb{R}^n \to \mathbb{R}^n : v \mapsto C + \gamma Pv \]
\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).
